Seasonality in governing upper-ocean dynamics at submesoscales

### 2016-05-09 writeup/rocha_etal.tex
Fixes typos

Recent interest in upper-ocean dynamics has focused on the strong seasonal
cycle of shallow baroclinic instabilities and their role in submesoscale (1-100 km)
turbulence and mesoscale modulation \citep{sasaki_etal2014,qiu_etal2014,
callies_etal2015, thompson_etal2016,buckingham_etal2016}. Contemporary studies
have also suggested that inertia-gravity waves contribute significantly
to the near-surface variability at scale submesoscales \citep{richman_etal2012,
buhler_etal2014,rocha_etal2016}.

Using the output of a $1/24^\circ$ global simulation, we show that the near-surface
expression of inertia-gravity waves undergo strong seasonal cycle that is out-of-phase
with the seasonal cycle of the balanced variability. This seasonal cycle is associated
with changes in the upper-ocean
stratification. Consistent with previous studies,
deep late Winter mixed-layers are prone to
shallow baroclinic instabilities that are roughly in geostrophic balance
and flux energy upscale \citep{sasaki_etal2014,callies_etal2016},
driving a mild seasonal modulation of the mesoscales \citep{sasaki_etal2014,qiu_etal2014}.
The horizontally divergent part of the flow, however, peaks in late Summer/early Fall,
when the upper-ocean is strongly stratified. Hence these results suggest a
strong seasonal modulation of the dominant upper-ocean submesoscale dynamics:
quasi-balanced turbulence in late Winter/early Spring and
quasi-linear inertia-gravity waves in late Summer/early Fall.

@@

%%% End of body of article:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% Appendix A: Here Is Appendix Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS

>>>>

Recent interest in upper-ocean dynamics has focused on the strong seasonal
cycle of shallow baroclinic instabilities and their role in submesoscale (1-100 km)
turbulence and mesoscale modulation \citep{sasaki_etal2014,qiu_etal2014,
callies_etal2015, thompson_etal2016,buckingham_etal2016}. Contemporary studies
have also suggested that inertia-gravity waves contribute significantly
to the near-surface variability at submesoscales \citep{richman_etal2012,
buhler_etal2014,rocha_etal2016}.

Using the output of a $1/24^\circ$ global simulation, we show that the near-surface
expression of inertia-gravity waves undergoes a strong seasonal cycle that is out-of-phase
with the seasonal cycle of the balanced variability. This seasonal cycle is associated
with changes in the upper-ocean
stratification. Consistent with previous studies,
deep late Winter mixed-layers are prone to
shallow baroclinic instabilities that are roughly in geostrophic balance
and flux energy upscale \citep{sasaki_etal2014,callies_etal2016},
driving a mild seasonal modulation of the mesoscales \citep{sasaki_etal2014,qiu_etal2014}.
The horizontally divergent part of the flow, however, peaks in late Summer/early Fall,
when the upper-ocean is strongly stratified. Hence these results suggest a
strong seasonal modulation of the dominant upper-ocean submesoscale dynamics:
quasi-balanced turbulence in late Winter/early Spring and
quasi-linear inertia-gravity waves in late Summer/early Fall.

@@

%%% End of body of article:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% Appendix A: Here Is Appendix Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS
